Commutative character sheaves and geometric types for supercuspidal representations

### 2017-05-10 Geometric types.tex
OK, I think this is all we need ...

In previous work \cite{cunningham-roe:13a}, we generalized the function-sheaf dictionary to
smooth commutative group schemes $G$, allowing for non-connected groups.
We gave a description of the category $\CS(G)$ in this context, as well
as an epimorphism $\TrFrob{G} : \CSiso{G} \to G(k)^*$.
In contrast to the connected case, $\TrFrob{G}$ may have nontrivial kernel;
we gave an explicit description of its kernel as $\Hh^2(\pi_0(\bG), \EEx)^{\Frob{}}$ \cite{cunningham-roe:13a}*{Thm. 3.6}.

@@

In \cite{cunningham-roe:13a}*{Thm. 3.6}, we showed that $\TrFrob{G} : \CSiso{G} \to G(k)^*$ is surjective and
explicitly computed its kernel.  In this section, we show that the corresponding map
$\TrFrob{G} : \CCSiso{G} \to G(k)^*$ for commutative character sheaves is an isomorphism.
We begin by reinterpreting Definition \ref{def:CCScom} in terms of cocycles.

@@

For general smooth commutative group schemes, we use Lemma \ref{lem:conncomm} and the snake lemma, as in the proof of
\cite{cunningham-roe:13a}*{Thm. 3.6}
\end{proof}

@@

In this section we give an equivalence of categories between $\CS(G\ab)$ and $\CSab(G)$ and use it to describe
the pullback functor $q^* : \CS(G\ab) \to \CS(G)$ in terms of the forgetful functor $\CSab(G) \to \CS(G)$.

In order to study commutative character sheaves, we need some auxiliary categories.

@@

Let $\Loc(G)$ and $\Loc(G\ab)$ be the categories of Weil local systems on $G$ and $G\ab$, respectively.
%
Let $\Loc_{G\der}(G)$ be the category of $G\der$-equivariant Weil local systems on $G$, whose definition we now recall.
Let $n : G\der\times G\to G$ be the restriction of $m : G\times G\to G$ to $G\der\times G$,
let $p : G\der\times G \to G$ be projection to the second component, and let $s: G \to G\der\times G$ be given by $s(g) = (1,g)$.
Then the quotient $q : G \to G\ab$ is a regular epimorphism of smooth group schemes with kernel pair $(n,p)$.
\[
\begin{tikzcd}
G\der\times G
 \arrow[shift left=1]{r}{n}
  \arrow[shift right=1,swap]{r}{p}
&
G 
\arrow{r}{q}
& 
G\ab
\end{tikzcd}
\]
Consider the morphisms
\[
\begin{tikzcd}
G\der \times G\der \times G 
\arrow[shift left=2]{r}{b_1, b_2, b_3} 
\arrow{r}{}
\arrow[shift right=2]{r}{} 
& G\der \times G 
\arrow[shift left=1]{r}{n}
\arrow[shift right=1]{r}[swap]{p}
 & G 
\end{tikzcd}
\]
defined by 
\begin{align*}
b_1(h_1,h_2,g) &= (h_1h_2,g) \\
b_2(h_1,h_2,g) &= (h_1,h_2g) \\
b_3(h_1,h_2,g) &= (h_2,g).
\end{align*}
Note that
\begin{align*}
n\circ b_1 &= n\circ b_2 \\
n\circ b_3 &= p\circ b_2 \numberthis \label{eqn:bap}\\
p\circ b_1 &= p\circ b_3.
\end{align*}
Define $s : G\to G\der\times G$ by $s(g) = (1,g)$.
A $G\der$-equivariant Weil local sytem on $G$ is a Weil local system $\cs{L}$ on $G$ together with an isomorphism  
\[
\nu : n^*\cs{L} \to p^*\cs{L}
\] 
of Weil local systems on $G\der\times G$ such that 
\begin{equation}\label{E1}
s^*(\nu) = \id_{\cs{L}}
\end{equation}
and such that the following diagram of isomorphisms of local systems on $G\der\times G\der\times G$ commutes. 
\begin{equation}\label{E2}
\begin{tikzcd}
\ &  \arrow{dl}{n\circ b_1 = n\circ b_2}  b_2^*  a^*\, \mathcal{L} \arrow{rr}{b_2^*(\nu)} && b_2^* p^*\, \mathcal{L} \arrow{dr}[swap]{p\circ b_2 = a\circ b_3} & \\
b_1^* n^*\, \mathcal{L} \arrow{dr}{b_1^*(\nu)} &&&&   \arrow{dl}[swap]{b_3^*(\nu)} b_3^* a^*\, \mathcal{L} \\
& b_1^* p^*\, \mathcal{L}  && \arrow{ll}[swap]{p\circ b_3 = p\circ b_1} b_3^* p^*\, \mathcal{L} & 
\end{tikzcd}
\end{equation}
%In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from equations \eqref{eqn:bap}; so, for example, the top left isomorphism comes from $b_1^* n^* \iso b_2^* n^*$ since $n\circ b_1 = n\circ b_2$.
%On stalks, this condition is ...
%\[
%\begin{tikzcd}
%\ &  \cs{L}_{h_1\cdot(h_2\cdot g)} \arrow{r}{\nu_{h_1,h_2\cdot g}} & \cs{L}_{h_2\cdot g} & \\
%\cs{L}_{(h_1 h_2) \cdot g} \arrow{dr}[swap]{\nu_{(h_1h_2),g}} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{\nu_{h_2,g}} \cs{L}_{h_2\cdot g} \\
%& \cs{L}_g \arrow[equal]{r} & \cs{L}_g & 
%\end{tikzcd}
%\]
Morphisms of $H$-equivariant Weil local systems $(\cs{L},\nu)\to (\cs{L}',\nu')$ are morphisms of Weil local systems $\alpha: \cs{L}\to \cs{L}'$ for which the diagram
\begin{equation}\label{E3}
\begin{tikzcd}
\arrow{d}[swap]{\nu} n^*\cs{L} \arrow{r}{n^*(\alpha)} & n^*\cs{L}' \arrow{d}{\nu'} \\
p^*\cs{L} \arrow{r}{p^*(\alpha)} & p^*\cs{L}'
\end{tikzcd}
\end{equation}
commutes.
This defines $\Loc_{G\der}(G)$, the category of $G\der$-equivariant Weil local systems on $G$.
The reader will recognize this notion as the Weil local system version of equivariant sheaves for the action $n$ of $G\der$ on $G$, as can be found, for example, in \cite{bernstein-lunts:equivariant}*{0.2}.

@@

\begin{lemma}
Categories $\CS\der(G)$ and $\CS\ab(G)$ are equivalent.
\end{lemma}

\begin{proof}
Let $i\der : G\der \to G$ be the kernel of $q:G \to G\ab$ and define $j : G\der \to G\der\times G$ by $j(h) = (h,1_G)$. 
If $(\cs{L},\mu,\nu)\in \CS\der(G)$ then $j^*(\nu) : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ is an isomorphism. 
This defines a functor on objects by
\[
\begin{array}{rcl}
\CS\der(G) &\to& \CSab(G) \\
(\cs{L},\mu,\nu) &\mapsto& (\cs{L},\mu,j^*(\nu))
\end{array}
\]
and on morphisms, trivially.
It is easy to verify that morphisms that commute with $\mu$ and $\nu$ also commute with $\mu$ and $j^*(\nu)$.
Define $k: G\der\times G\to G\times G$ by $k(h,g) = (i\der(h),g)$.
Then for $(\cs{L},\mu,\beta) \in \CSab(G)$, define $\nu : n^*\cs{L} \to p^*\cs{L}$ by the following diagram.
\[
\begin{tikzcd}
& n^* \cs{L} \arrow{dl}{m\circ k = n} \arrow{r}{\nu} & p^*\cs{L} &  \\ 
k^* m^* \cs{L} \arrow{dr}{k^*(\mu)} &&& (\EE)_{G\der} \boxtimes \cs{L} \arrow[equal]{ul} \\
& k^*(\cs{L}\boxtimes\cs{L}) \arrow[equal]{r} & \cs{L}\vert_{G\der}\boxtimes \cs{L} \arrow{ur}{\beta\boxtimes \id_\cs{L}}
\end{tikzcd}
\]
Then $(\cs{L},\mu,\nu)\in \CS\der(G)$ maps to $(\cs{L},\mu,\beta)$.
It now follows that $\CS\der(G) \to \CSab(G)$ is an equivalence. \todo{Add more detail to this proof?}
\end{proof}

Set $G^2 = G\times G$. Then $G^2\der = G\der\times G\der$ and $G^2\ab = G\ab\times G\ab$.

@@

\begin{proof} 
Define
\begin{align*}
d : H\times H\times G\times G &\to H\times G\times H\times G \\
(h_1,h_2,g_1,g_2) &\mapsto (h_1, g_1, h_2, g_2)\\
a_2 : H\times G\times H\times G &\to G\times G \\
(h_1,g_1,h_2,g_2) &\mapsto (h_1g_1, h_2g_2) \\
p_2 : H\times G\times H\times G &\to G\times G \\
(h_1,g_1,h_2,g_2) &\mapsto ( g_1,g_2) \\
\theta_2 : H \times G \times H \times G &\to H \times G \times H \times G \\
(h_1,g_1,h_2,g_2) &\mapsto (h_2,g_2,h_1,g_1).
\end{align*}
The following diagram defines the isomorphisms needed to see that both $m^*\cs{L}$ and $\cs{L}\boxtimes\cs{L}$ are $H\times H$-equivariant Weil local systems.
\[
\begin{tikzcd}[column sep=40]
\arrow{d}[swap]{a_2^*(\mu)} a_2^* (m^*\cs{L}) \arrow[dashed]{r} 
	& \arrow{d}{p_2^*(\mu)} p_2^*(m^*\cs{L})\\
\arrow{d}[swap]{a_2= (a\times a)\circ d} a_2^*(\cs{L}\boxtimes\cs{L}) \arrow[dashed]{r} 
	& \arrow{d}{p_2= (p\times p)\circ d} p_2^*(\cs{L}\boxtimes\cs{L}) \\
%d^* (a\times a)^* (\cs{L}\boxtimes\cs{L}) & d^* (p\times p)^* (\cs{L}\boxtimes\cs{L}) \\
d^* (a^*\cs{L}\boxtimes a^*\cs{L}) \arrow{r}{d^*(\nu\boxtimes \nu)}& d^*(p^*\cs{L}\boxtimes p^*\cs{L}) 
\end{tikzcd}
\]
The dashed arrows both satisfy \eqref{E1} and \eqref{E2} as they apply here.
This diagram also shows that $\mu : m^*\cs{L} \to \cs{L}\boxtimes \cs{L}$ is a morphism of equivariant sheaves, since it satisfies \eqref{E3} as it applies here.
\end{proof}

@@

Consider the functor
\[
q^* : \CS(G\ab) \to \CS(G)
\]
given on objects by $(\cs{L}\ab,\mu\ab) \mapsto (q^*\cs{L}\ab, (q^2)^* \mu\ab)$ where $q^2= q\times q$; this is an instance of \cite{cunningham-roe:13a}*{Lemma 1.4}.
To see that $(q^*\cs{L}\ab, (q^2)^* \mu\ab)$ is indeed a linear character sheaf on $G$,
verify \cite{cunningham-roe:13a}*{CS.3}. %, arguing as in \cite{cunningham-roe:13a}.
The linear character sheaf $(\cs{L},\mu)$ on $G$ comes equipped with a canonical isomorphism $\nu : n^* \cs{L} \to p^* \cs{L}$ defined by the following diagram of isomorphisms.
\[
\begin{tikzcd}[column sep=40]
n^*\cs{L} \arrow[equal]{d} \arrow{r}{\nu} &  \arrow[equal]{d} p^*\cs{L} \\
n^* ( q^*\cs{L}\ab) \arrow{r}{q\circ n = q\circ p}
& p^* (q^*\cs{L}\ab)
\end{tikzcd}
\]
Then $(\cs{L}, \mu,\nu)$ is an object in $\CS\der(G)$.
If $\alpha : (\cs{L}\ab,\mu\ab) \to (\cs{L}\ab',\mu\ab')$ is a morphism in $\CS(G\ab)$, 
then $q^*(\alpha\ab) : (\cs{L},\mu) \to (\cs{L}',\mu')$ satisfies \cite{cunningham-roe:13a}*{CS4}, so $\alpha$ is a morphism in $\CS(G)$.
These simple observations define the comparison functor
\[
q\ab^* : \CS(G\ab) \to \CS\der(G)
\]
and show that the functor $q^* : \CS(Q) \to \CS(G)$ factors according to the following commuting diagram of functors
\begin{equation}\label{qH}
\begin{tikzcd}
\CS(G) &\arrow{l}[swap]{q^*} 
\CS(G\ab) \arrow{dl}{q\ab^*}\\
\arrow{u}{\text{forget}} \CS\der(G). & 
\end{tikzcd}
\end{equation}
The definition of $q\ab^* : \CS(G\ab)\to \CS\der(G)$ will be revisited in the proof of the following result.

We may now begin to relate $\CSab(G)$ to $\CS(G\ab)$ via the quotient map $q : G \to G\ab$.

%\fi
%%%%%%%%%%%%%%%%%

\begin{proposition} \label{prop:CSGabab}
Suppose $G$ is a smooth group scheme.  
Then pullback along $q : G \to G\ab$ defines an equivalence $q\ab^*: \CS(G\ab) \to \CSab(G)$.
\end{proposition}
\begin{proof}
It now follows from descent theory that the comparison functor $L : \Loc(G\ab) \to \Loc_{G\der}(G)$ is an equivalence: argue as in \cite{Vistoli:notes}*{Thm 4.46} for example. 
For $\cs{L}\ab\in \Loc(G\ab)$, we may write $L(\cs{L}\ab) = (\cs{L}, \nu)$, where $\cs{L} = q^*(\cs{L}\ab)$ and $\nu : n^*\cs{L}  \to p^*\cs{L}$ is an isomorphism. 
Observe that $L$ followed by the forgetful functor $\Loc_{G\der}(G)\to \Loc(G)$ coincides with $q^*: \Loc(G\ab)\to \Loc(G)$. 
%
Now set $G^2 \ceq G\times G$, so $G^2\ab =  G\ab \times G\ab$ and $G^2\der = G\der \times G\der$. Let $q_2 : G^2 \to G^2\ab$ be the abelianization quotient.  
Let $L_2 : \Loc(G^2\ab) \to \Loc_{G^2\der}(G^2)$ be the comparison functor for the quotient $q^2  : G^2 \to G^2\ab$. \todo{Add reference to Lemma 3.3}
Then $L_2$ is also an equivalence since $q_2$ is also a $G^2\der$-torsor.

Consider the functor
\[
\begin{array}{rcl}
\CS(G\ab) &\to& \CSab'(G) \\
(\cs{L}\ab,\mu\ab) &\mapsto& (L(\cs{L}\ab), L_2(\mu\ab))
\end{array}
\]
Since both $L$ and $L_2$ are equivalences, this functor $\CS(G\ab) \to \CSab'(G)$ is an equivalence of categories. \todo{I'm a bit wary of constructing an equivalence componentwise in this way; how does it show that the result is full and faithful since it's just talking about objects?}

(I moved the rest...)
\end{proof}

@@

\begin{corollary}
If $G$ is a smooth group scheme and $(\cs{L},\mu)$ is a character sheaf on $G$ with trivial restriction to $G\der$,
then the set of isomorphism classes of objects in $\CS(G\ab)$ mapping to $(\cs{L},\mu)$ under $q^*$ is a principal homogeneous space
for $C$.
\end{corollary}
\begin{proof}
By Proposition~\ref{prop:CSGabab}, it suffices to find the set of isomorphism classes in $\CSab(G)$ mapping to
$(\cs{L},\mu)$ under the forgetful functor.  By the previous corollary this set is nonempty.
If $(\cs{L},\mu,\beta)$ and $(\cs{L},\mu,\beta')$ both map to $(\cs{L},\mu)$, then $\beta' \circ \beta^{-1}$ is an
automorphism of the constant sheaf on $G\der$.  Conversely, if $\varphi$ is an automorphism of $(\EE)_{G\der}$
and $(\cs{L},\mu,\beta) \in \CSab(G)$ then $(\cs{L},\mu,\varphi \circ \beta) \in \CSab(G)$.  By \cite{cunningham-roe:13a}*{Thm. 3.9},
the automorphism group is isomorphic to $\Hom(\pi_0(\bar{G}\der)_{\Frob{}}, \EEx)$.  Finally, we note that any
automorphism $\alpha$ of $(\cs{L},\mu) \in \CS(G)$ defines an isomorphism $(\cs{L},\mu,\beta \circ \alpha|_{G\der}) \to (\cs{L},\mu,\beta)$.
Applying \cite{cunningham-roe:13a}*{Thm. 3.9} again yields the desired result.
\end{proof}

@@

We start with a method that will allow us to situate the diagram in Definition \ref{def:CCS} within $\CSab(G \times G)$.

>>>>

In previous work \cite{cunningham-roe:13a}, we generalized the function-sheaf dictionary to
smooth commutative group schemes $G$, allowing for non-connected groups.
We gave a description of the category $\CS(G)$ in this context, as well
as an epimorphism $\TrFrob{G} : \CSiso{G} \to G(k)^*$.
In contrast to the connected case, $\TrFrob{G}$ may have nontrivial kernel;
we gave an explicit description of its kernel as $\Hh^2(\pi_0(\bG), \EEx)^{\Frob{}}$ \cite{cunningham-roe:13a}*{Theorem 3.6}.

@@

In \cite{cunningham-roe:13a}*{Theorem 3.6}, we showed that $\TrFrob{G} : \CSiso{G} \to G(k)^*$ is surjective and
explicitly computed its kernel.  In this section, we show that the corresponding map
$\TrFrob{G} : \CCSiso{G} \to G(k)^*$ for commutative character sheaves is an isomorphism.
We begin by reinterpreting Definition \ref{def:CCScom} in terms of cocycles.

@@

For general smooth commutative group schemes, we use Lemma \ref{lem:conncomm} and the snake lemma, as in the proof of
\cite{cunningham-roe:13a}*{Theorem 3.6}
\end{proof}

@@

In this section we give an equivalence of categories between $\CS(G\ab)$ and $\CSab(G)$ and use it to describe
the pullback functor $q^* : \CS(G\ab) \to \CS(G)$ in terms of the forgetful functor $\CSab(G) \to \CS(G)$.
But first, in order to study commutative character sheaves, we need some auxiliary categories.

@@

Let $\Loc(G)$ and $\Loc(G\ab)$ be the categories of Weil local systems on $G$ and $G\ab$, respectively.
%
Let $\Loc\der(G)$ be the category of $G\der$-equivariant Weil local systems on $G$, whose definition we now recall.
Let $n : G\der\times G\to G$ be the restriction of $m : G\times G\to G$ to $G\der\times G$,
let $p : G\der\times G \to G$ be projection to the second component, and let $s: G \to G\der\times G$ be given by $s(g) = (1,g)$.
Then the quotient $q : G \to G\ab$ is a regular epimorphism of smooth group schemes with kernel pair $(n,p)$.
\[
\begin{tikzcd}
G\der\times G
 \arrow[shift left=1]{r}{n}
  \arrow[shift right=1,swap]{r}{p}
&
G 
\arrow{r}{q}
& 
G\ab
\end{tikzcd}
\]
Consider the morphisms
\[
\begin{tikzcd}
G\der \times G\der \times G 
\arrow[shift left=2]{r}{b_1, b_2, b_3} 
\arrow{r}{}
\arrow[shift right=2]{r}{} 
& G\der \times G 
\arrow[shift left=1]{r}{n}
\arrow[shift right=1]{r}[swap]{p}
 & G 
\end{tikzcd}
\]
defined by 
\begin{align*}
b_1(h_1,h_2,g) &= (h_1h_2,g) \\
b_2(h_1,h_2,g) &= (h_1,h_2g) \\
b_3(h_1,h_2,g) &= (h_2,g).
\end{align*}
Note that
\begin{align*}
n\circ b_1 &= n\circ b_2 \\
n\circ b_3 &= p\circ b_2 \numberthis \label{eqn:bap}\\
p\circ b_1 &= p\circ b_3.
\end{align*}
Define $s : G\to G\der\times G$ by $s(g) = (1,g)$.
A $G\der$-equivariant Weil local sytem on $G$ is a Weil local system $\cs{L}$ on $G$ together with an isomorphism  
\[
\nu : n^*\cs{L} \to p^*\cs{L}
\] 
of Weil local systems on $G\der\times G$ such that 
\begin{equation}\label{E1}
s^*(\nu) = \id_{\cs{L}}
\end{equation}
and such that the following diagram of isomorphisms of local systems on $G\der\times G\der\times G$ commutes. 
\begin{equation}\label{E2}
\begin{tikzcd}
\ &  \arrow{dl}{n\circ b_1 = n\circ b_2}  b_2^*  a^*\, \mathcal{L} \arrow{rr}{b_2^*(\nu)} && b_2^* p^*\, \mathcal{L} \arrow{dr}[swap]{p\circ b_2 = a\circ b_3} & \\
b_1^* n^*\, \mathcal{L} \arrow{dr}{b_1^*(\nu)} &&&&   \arrow{dl}[swap]{b_3^*(\nu)} b_3^* a^*\, \mathcal{L} \\
& b_1^* p^*\, \mathcal{L}  && \arrow{ll}[swap]{p\circ b_3 = p\circ b_1} b_3^* p^*\, \mathcal{L} & 
\end{tikzcd}
\end{equation}
%In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from equations \eqref{eqn:bap}; so, for example, the top left isomorphism comes from $b_1^* n^* \iso b_2^* n^*$ since $n\circ b_1 = n\circ b_2$.
%On stalks, this condition is ...
%\[
%\begin{tikzcd}
%\ &  \cs{L}_{h_1\cdot(h_2\cdot g)} \arrow{r}{\nu_{h_1,h_2\cdot g}} & \cs{L}_{h_2\cdot g} & \\
%\cs{L}_{(h_1 h_2) \cdot g} \arrow{dr}[swap]{\nu_{(h_1h_2),g}} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{\nu_{h_2,g}} \cs{L}_{h_2\cdot g} \\
%& \cs{L}_g \arrow[equal]{r} & \cs{L}_g & 
%\end{tikzcd}
%\]
Morphisms of $H$-equivariant Weil local systems $(\cs{L},\nu)\to (\cs{L}',\nu')$ are morphisms of Weil local systems $\alpha: \cs{L}\to \cs{L}'$ for which the diagram
\begin{equation}\label{E3}
\begin{tikzcd}
\arrow{d}[swap]{\nu} n^*\cs{L} \arrow{r}{n^*(\alpha)} & n^*\cs{L}' \arrow{d}{\nu'} \\
p^*\cs{L} \arrow{r}{p^*(\alpha)} & p^*\cs{L}'
\end{tikzcd}
\end{equation}
commutes.
This defines $\Loc\der(G)$, the category of $G\der$-equivariant Weil local systems on $G$.
The reader will recognize this notion as the Weil local system version of equivariant sheaves for the action $n$ of $G\der$ on $G$, as can be found, for example, in \cite{bernstein-lunts:equivariant}*{0.2}.

@@

\begin{lemma}\label{lemma:nubeta}
Categories $\CS\der(G)$ and $\CS\ab(G)$ are equivalent.
\end{lemma}

\begin{proof}
Let $i\der : G\der \to G$ be the kernel of $q:G \to G\ab$ and define $j : G\der \to G\der\times G$ by $j(h) = (h,1_G)$. 
If $(\cs{L},\mu,\nu)\in \CS\der(G)$ then $j^*(\nu) : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ is an isomorphism. 
This defines a functor on objects by
\[
\begin{array}{rcl}
\CS\der(G) &\to& \CSab(G) \\
(\cs{L},\mu,\nu) &\mapsto& (\cs{L},\mu,j^*(\nu))
\end{array}
\]
and on morphisms, trivially.
It is easy to verify that morphisms that commute with $\mu$ and $\nu$ also commute with $\mu$ and $j^*(\nu)$.
Define $k: G\der\times G\to G\times G$ by $k(h,g) = (i\der(h),g)$.
Then for $(\cs{L},\mu,\beta) \in \CSab(G)$, define $\nu : n^*\cs{L} \to p^*\cs{L}$ by the following diagram.
\[
\begin{tikzcd}
& n^* \cs{L} \arrow{dl}{m\circ k = n} \arrow{r}{\nu} & p^*\cs{L} &  \\ 
k^* m^* \cs{L} \arrow{dr}{k^*(\mu)} &&& (\EE)_{G\der} \boxtimes \cs{L} \arrow[equal]{ul} \\
& k^*(\cs{L}\boxtimes\cs{L}) \arrow[equal]{r} & \cs{L}\vert_{G\der}\boxtimes \cs{L} \arrow{ur}{\beta\boxtimes \id_\cs{L}}
\end{tikzcd}
\]
Then $(\cs{L},\mu,\nu)\in \CS\der(G)$ maps to $(\cs{L},\mu,\beta)$.
It now follows that $\CS\der(G) \to \CSab(G)$ is an equivalence. \todo{Should we add more detail to this proof?}
\end{proof}

Set $G^2 = G\times G$, so $G^2\der = G\der\times G\der$ and $G^2\ab = G\ab\times G\ab$.
Likewise define $n^2 : G\der^2 \times G^2 \to G^2$ and $p^2 : G\der^2\times G \to G$.

@@

\begin{proof} 
Define
\begin{align*}
d : G\der\times G\der\times G\times G &\to G\der\times G\times G\der\times G \\
(h_1,h_2,g_1,g_2) &\mapsto (h_1, g_1, h_2, g_2)\\
n_2 : G\der\times G\times G\der\times G &\to G\times G \\
(h_1,g_1,h_2,g_2) &\mapsto (h_1g_1, h_2g_2) \\
p_2 : G\der\times G\times G\der\times G &\to G\times G \\
(h_1,g_1,h_2,g_2) &\mapsto ( g_1,g_2). %\\
%\theta_2 : H \times G \times H \times G &\to H \times G \times H \times G \\
%(h_1,g_1,h_2,g_2) &\mapsto (h_2,g_2,h_1,g_1).
\end{align*}
The following diagram defines the isomorphisms needed to see that both $m^*\cs{L}$ and $\cs{L}\boxtimes\cs{L}$ are $G\der^2$-equivariant Weil local systems.
\[
\begin{tikzcd}[column sep=40]
\arrow{d}[swap]{n_2^*(\mu)} n_2^* (m^*\cs{L}) \arrow[dashed]{r} 
	& \arrow{d}{p_2^*(\mu)} p_2^*(m^*\cs{L})\\
\arrow{d}[swap]{n_2= n^2\circ d} n_2^*(\cs{L}\boxtimes\cs{L}) \arrow[dashed]{r} 
	& \arrow{d}{p_2= p^2\circ d} p_2^*(\cs{L}\boxtimes\cs{L}) \\
%d^* (n\times n)^* (\cs{L}\boxtimes\cs{L}) & d^* (p\times p)^* (\cs{L}\boxtimes\cs{L}) \\
d^* (n^*\cs{L}\boxtimes n^*\cs{L}) \arrow{r}{d^*(\nu\boxtimes \nu)}& d^*(p^*\cs{L}\boxtimes p^*\cs{L}) 
\end{tikzcd}
\]
The dashed arrows both satisfy \eqref{E1} and \eqref{E2} as they apply here.
This diagram also shows that $\mu : m^*\cs{L} \to \cs{L}\boxtimes \cs{L}$ is a morphism of equivariant sheaves, since it satisfies \eqref{E3} as it applies here.
\end{proof}

@@

If $\cs{L}\ab\in \Loc(G\ab)$ then $q^*\cs{L}\ab\in \Loc(G)$ comes equipped with a canonical isomorphism $\nu(\cs{L}\ab) : n^* \cs{L} \to p^* \cs{L}$ defined by the following diagram of isomorphisms.
\[
\begin{tikzcd}[column sep=40]
n^*\cs{L} \arrow[equal]{d} \arrow{r}{\nu(\cs{L}\ab)} &  \arrow[equal]{d} p^*\cs{L} \\
n^* ( q^*\cs{L}\ab) \arrow{r}{q\circ n = q\circ p}
& p^* (q^*\cs{L}\ab)
\end{tikzcd}
\]
Then $(q^*\cs{L}\ab,\nu(\cs{L}\ab))$ satisfies \eqref{E1} and \eqref{E2}, so $(q^*\cs{L}\ab,\nu(\cs{L}\ab))$ is an object in $\Loc\der(G)$.
Moreover, if $\alpha\ab : \cs{L}\ab \to \cs{L}\ab$ is a morphism in $\Loc(G\ab)$ then $q^*(\alpha\ab)$ satisfies the condition in \eqref{E3}, so $q^*(\alpha\ab)$ is a morphism in $\Loc\der(G)$.
This defines the functor
\[
L : \Loc(G\ab)\to \Loc\der(G)
\]

\begin{lemma}\label{lemma:descent}
The functor $L : \Loc(G\ab)\to \Loc\der(G)$ is an equivalence.
\end{lemma}
\begin{proof}
The quotient $q : G \to G\ab$ is an $G\der$-torsor in the fppf topology by \cite{demazure:SGA3-VIA}*{Thm. 3.2}, and thus an $G\der$-torsor in the fpqc topology.
The lemma is now a result from descent theory, arguing as in \cite{Vistoli:notes}*{Theorem 4.46} for example. 
\end{proof}

Consider the functor
\[
q^* : \CS(G\ab) \to \CS(G)
\]
given on objects by $(\cs{L}\ab,\mu\ab) \mapsto (q^*\cs{L}\ab, (q^2)^* \mu\ab)$; this is an instance of \cite{cunningham-roe:13a}*{Lemma 1.4}.
To see that $(q^*\cs{L}\ab, (q^2)^* \mu\ab)$ is indeed a linear character sheaf on $G$,
verify \cite{cunningham-roe:13a}*{CS.3}. %, arguing as in \cite{cunningham-roe:13a}.
Now set $L(\cs{L}\ab) = (\cs{L},\nu)$, where $L : \Loc(G\ab) \to \Loc\der(G)$ is the comparison functor above, so $\cs{L} = q^*\cs{L}\ab$ and $\nu = \nu(\cs{L}\ab)$.
Then $(\cs{L}, \mu,\nu)$ is an object in $\CS\der(G)$.
If $\alpha : (\cs{L}\ab,\mu\ab) \to (\cs{L}\ab',\mu\ab')$ is a morphism in $\CS(G\ab)$, 
then $q^*(\alpha\ab) : (\cs{L},\mu) \to (\cs{L}',\mu')$ satisfies \cite{cunningham-roe:13a}*{CS4}, so $\alpha$ is a morphism in $\CS(G)$.
These simple observations define the comparison functor
\[
q\ab^* : \CS(G\ab) \to \CS\der(G)
\]
and also show that the functor $q^* : \CS(G\ab) \to \CS(G)$ factors according to the following commuting diagram of functors
\begin{equation}\label{qH}
\begin{tikzcd}
\CS(G) &\arrow{l}[swap]{q^*} 
\CS(G\ab) \arrow{dl}{q\ab^*}\\
\arrow{u}{\text{forget}} \CS\der(G). & 
\end{tikzcd}
\end{equation}
The definition of $q\ab^* : \CS(G\ab)\to \CS\der(G)$ will be revisited in the proof of the following result.
We may now relate $\CSab(G)$ to $\CS(G\ab)$ via the quotient map $q : G \to G\ab$.

\begin{proposition} \label{prop:CSGabab}
Suppose $G$ is a smooth group scheme.  
Then pullback along $q : G \to G\ab$ defines an equivalence $\CS(G\ab) \to \CSab(G)$.
\end{proposition}
\begin{proof}
In light of Lemma~\ref{lemma:nubeta}, it suffices to prove that the comparison functor $q\ab^* : \CS(G\ab) \to \CS\der(G)$ is an equivalence. 
Let $L^2 : \Loc(G^2\ab) \to \Loc\der(G^2)$ be the comparison functor for the quotient $q^2  : G^2 \to G^2\ab$. 
Then $L^2$ is also an equivalence by Lemma~\ref{lemma:descent}.
Using Lemma~\ref{lem:HH}, we may rewrite the comparison functor $q\ab^*$ on objects by
\[
\begin{array}{rcl}
\CS(G\ab) &\to& \CS\der(G) \\
(\cs{L}\ab,\mu\ab) &\mapsto& (L(\cs{L}\ab), L^2(\mu\ab))
\end{array}
\]
and on morphisms by $\alpha \mapsto L(\alpha)$.
The proposition now follows from the fact that both $L$ and $L^2$ are equivalences.
\end{proof}

@@

\begin{corollary}
If $G$ is a smooth group scheme and $(\cs{L},\mu)$ is a character sheaf on $G$ with trivial restriction to $G\der$,
then the set of isomorphism classes of objects in $\CS(G\ab)$ mapping to $(\cs{L},\mu)$ under $q^*$ is a principal homogeneous space
for $C$.
\end{corollary}
\begin{proof}
By Proposition~\ref{prop:CSGabab}, it suffices to find the set of isomorphism classes in $\CSab(G)$ mapping to
$(\cs{L},\mu)$ under the forgetful functor.  By the previous corollary this set is nonempty.
If $(\cs{L},\mu,\beta)$ and $(\cs{L},\mu,\beta')$ both map to $(\cs{L},\mu)$, then $\beta' \circ \beta^{-1}$ is an
automorphism of the constant sheaf on $G\der$.  Conversely, if $\varphi$ is an automorphism of $(\EE)_{G\der}$
and $(\cs{L},\mu,\beta) \in \CSab(G)$ then $(\cs{L},\mu,\varphi \circ \beta) \in \CSab(G)$.  By \cite{cunningham-roe:13a}*{Theorem 3.9},
the automorphism group is isomorphic to $\Hom(\pi_0(\bar{G}\der)_{\Frob{}}, \EEx)$.  Finally, we note that any
automorphism $\alpha$ of $(\cs{L},\mu) \in \CS(G)$ defines an isomorphism $(\cs{L},\mu,\beta \circ \alpha|_{G\der}) \to (\cs{L},\mu,\beta)$.
Applying \cite{cunningham-roe:13a}*{Theorem 3.9} again yields the desired result.
\end{proof}

@@

We start with a method that will allow us to situate the diagram in Definition \ref{def:CCS} within $\CSab(G^2)$.
